On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-09 manuscripts/IEEE/final_submission.tex
discusion final edits

@@

We close with some challenges left open by our work. All of our conditions guaranteeing the uniqueness and stability of sparse representations have only been proven sufficient; there therefore remains the open problem of extending them to necessary conditions, be they optimal lower bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds. On this last note in particular, we remark that our constants have been derived for deterministic ``worst-case'' noise, whereas the ``effective'' noise might be significantly reduced when sampled from a concentrated distribution. It would be interesting to see how drastically all conditions can be tightened (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.

Another interesting question that remains is: in what special cases is it efficient to check that a solution to Probs.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable)? Given the NP-hardness of computing our sufficient conditions for checking this in general, are the corresponding problems also computationally hard?  Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} guaranteeing that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?  % [*** Incorporate this open problem with more words ***]

>>>>

There are still several challenges left open by our work. All conditions here guaranteeing uniqueness and stability of sparse representations have only been shown sufficient; it remains open, therefore, to extend them to necessary conditions, be they optimal lower bounds on required sample size, conditions on the support set hypergraphs of generating codes, or tolerable error bounds. On this last note, we remark that our constants have been derived for deterministic ``worst-case" noise, whereas the ``effective" noise might be significantly reduced when sampled from a concentrated distribution. It would be interesting to see how drastically all conditions can be tightened (to practical benefit) by requiring only probabilistic guarantees in this way, or in the spirit of the discussion on sample complexity following our proof of Thm.~\ref{DeterministicUniquenessTheorem}.

Another interesting question that remains is for which special cases is it efficient to check that a solution to Probs.~\ref{InverseProblem} or \ref{OptimizationProblem} is unique (and stable). Given the NP-hardness of computing sufficient conditions for checking this in general, are the corresponding problems also computationally hard?  Finally, since substituting the norm $\|\cdot\|_0$ with $\|\cdot\|_1$ yields the same optimal sparse codes for dictionaries with large enough lower bounds \cite{eldar2012compressed}, is there a version of Thm.~\ref{SLCopt} certifying that Prob.~\ref{OptimizationProblem} can be solved while inferring sparse codes in this way?  % [*** Incorporate this open problem with more words ***]

@@
